---
title: A demo R blogdown post
author: demo
date: '2020-08-09'
slug: a-demo-r-blogdown-post
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2020-08-09T18:37:13+10:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

Quanteda is an R package for managing and analyzing text (https://quanteda.io/). One benefit of using quanteda is its powerful plot tools. You can easily plot a wordcloud graph for a set of documents, i.e. a corpus.

Here, we will use quanteda's build-in corpus, the *inaugural address corpus* to demonstrate how to plot a wordcloud graph.

**Step 1:** load quanteda package.

```{r message=FALSE}
library("quanteda")
```

**Step 2:** create a dfm (Document features matrix) by tokenize the corpus.

```{r}
my_tokens = tokens(data_corpus_inaugural, remove_punct = TRUE, remove_symbols = TRUE)
my_dfm = dfm(my_tokens, remove=stopwords(language = "en"))
```

**Step 3:** we use that dfm to plot a wordcloud graph.

```{r}
textplot_wordcloud(my_dfm, max_words=200)
```

There many more options for the plot. Please refer to [textplot_wordcloud](https://quanteda.io/reference/textplot_wordcloud.html) for more details.
